---
title: "Sentiment Regression"
author: "Charles Alba"
date: "2022-12-24"
output: pdf_document
---


```{r}
library(data.table)
library(ggplot2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(AER)
library(vcd)

data<-read.csv("sentimental_count.csv")
colnames(data)[which(names(data) == "X")] <- "Date"
data$Date<-as.character(data$Date)

covid<-read.csv("COVID_cases.csv")
covid$Date<-format(as.Date(covid$date), format="%m-%d")
covid$covid_cases_per_10000<-(covid$covid_cases_per_10000)

df<-merge(data,covid,by.x="Date",by.y="date",all.x = T)
df$t<-1:NROW(df)
```

# Analyzing Tweet Counts

## wAIC scores


```{r}
m0 <- glm(Tweets ~ t + covid_cases_per_10000, data=df, family = "poisson")
AIC(m0,k=2)
m1 <- glm(Tweets ~ t +lag(Tweets)+ covid_cases_per_10000,data=df, family = "poisson")
AIC(m1,k=3)
m2 <- glm(Tweets ~ t +(lag(Tweets))+ lag(Tweets,n=2L)+covid_cases_per_10000, data=df, family = "poisson")
AIC(m2,k=4)
m3 <- glm(Tweets ~ t +lag(Tweets)+(lag(Tweets,n=2L))+ lag(Tweets,n=3L)+covid_cases_per_10000, data=df, family = "poisson")
AIC(m3,k=5)
m4 <- glm(Tweets ~ t +(lag(Tweets,n=4L))+lag(Tweets,3L)+(lag(Tweets,2L))+ lag(Tweets)+covid_cases_per_10000, data=df, family = "poisson")
AIC(m4,k=6)
```

## Diagnostics

```{r}
acf(data$Tweets)
pacf(data$Tweets)
vif(m3)
dispersiontest(m3)
dispersiontest(m3, alternative = "less")

```
## Summary of results. 

```{r}
summary(m3)
```



# Analyzing Negative Sentiments 

## Setting wAIC 


```{r}
n0 <- glm(sentiment_NEG ~ t + covid_cases_per_10000, family="poisson", data=df)
AIC(n0,k=2)

n1 <- glm(sentiment_NEG ~ t + lag(sentiment_NEG)+covid_cases_per_10000, family="poisson", data=df)
AIC(n1,k=3)

n2 <- glm(sentiment_NEG ~ t + lag(sentiment_NEG)+(lag(sentiment_NEG,n=2L))+covid_cases_per_10000, family="poisson", data=df)
AIC(n2,k=4)


n3 <- glm(sentiment_NEG ~ t + lag(sentiment_NEG)+lag(sentiment_NEG,n=2L)+(lag(sentiment_NEG,n=3L))+covid_cases_per_10000, family="poisson", data=df)
AIC(n3,k=5)


```



## plotting diagnostics

```{r}
vif(n0)
dispersiontest(n0)
dispersiontest(n0, alternative = "less")
acf(data$sentiment_NEG)
pacf(data$sentiment_NEG)
```

## Getting summary

```{r}
summary(n0)
```


# Analyzing Tweets with Fear 

## Getting wAIC

```{r}
f0 <- glm(fear ~ t + covid_cases_per_10000, data=df, family="poisson")
AIC(f0,k=2)

f1 <- glm(fear ~ t + covid_cases_per_10000+lag(fear), data=df,family="poisson")
AIC(f1,k=3)


f2 <- glm(fear ~ t + covid_cases_per_10000+lag(fear)+lag(fear,n=2L), data=df,family="poisson")
AIC(f2,k=4)


f3 <- glm(fear ~ t + covid_cases_per_10000+lag(fear)+lag(fear,n=2L)+lag(fear,n=3L), data=df,family="poisson")
AIC(f3,k=5)
```


## Plotting diagnostics

```{r}
vif(f0)
dispersiontest(f0)
dispersiontest(f0,alternative = "less")
acf(data$fear)
pacf(data$fear)
```

## Getting summary

```{r}
summary(f0)
```

# Analyzing Sad Tweets 

## Getting wAIC

```{r}
s0 <- glm(sadness ~ t + covid_cases_per_10000, family="poisson", data=df)
AIC(s0,k=2)
s1 <- glm(sadness ~ t + covid_cases_per_10000+lag(sadness), family="poisson", data=df)
AIC(s1,k=3)
s2 <- glm(sadness ~ t + covid_cases_per_10000+lag(sadness)+lag(sadness,n=2L), family="poisson", data=df)
AIC(s2,k=4)
s3 <- glm(sadness ~ t + covid_cases_per_10000+lag(sadness)+lag(sadness,n=2L)+lag(sadness,n=3L), family="poisson", data=df)
AIC(s3,k=5)
s4 <- glm(sadness ~ t + covid_cases_per_10000+lag(sadness)+lag(sadness,n=2L)+lag(sadness,n=3L)+lag(sadness,n=4L), family="poisson", data=df)
AIC(s4,k=6)
```


## plotting diagnostics


```{r}
vif(s0)
dispersiontest(s0)
dispersiontest(s0,alternative = "less")
acf(data$sadness)
pacf(data$sadness)
```
## Getting summary.

```{r}
summary(s0)
```

# Analyzing Disgust Tweets

## Getting wAIC




```{r}
d0 <- glm(disgust ~ t + covid_cases_per_10000, family="poisson", data=df)
AIC(d0,k=2)

d1 <- glm(disgust ~ t + covid_cases_per_10000+lag(disgust), family="poisson", data=df)
AIC(d1,k=3)


d2 <- glm(disgust ~ t + covid_cases_per_10000+lag(disgust)+lag(disgust,n=2L), family="poisson", data=df)
AIC(d2,k=4)


d3 <- glm(disgust ~ t + covid_cases_per_10000+lag(disgust)+lag(disgust,n=2L)+lag(disgust,n=3L), family="poisson", data=df)
AIC(d3,k=5)

d4 <- glm(disgust ~ t + covid_cases_per_10000+lag(disgust)+lag(disgust,n=2L)+lag(disgust,n=3L)+lag(disgust,n=4L), family="poisson", data=df)
AIC(d4,k=6)
```

## Plotting diagnostics


```{r}
vif(d0)
dispersiontest(d0)
dispersiontest(d0,alternative = "less")
acf(data$disgust)
pacf(data$disgust)
```

## getting summary

```{r}
summary(d0)
```

# Analyzing Tweets with Anger 

## Getting wAiC

```{r}
a0 <- glm(anger ~ t + covid_cases_per_10000, family="poisson", data=df)
AIC(a0,k=2)

a1 <- glm(anger ~ t + covid_cases_per_10000+lag(anger), family="poisson", data=df)
AIC(a1,k=3)


a2 <- glm(anger ~ t + covid_cases_per_10000+lag(anger)+lag(anger,n=2L), family="poisson", data=df)
AIC(a2,k=4)


a3 <- glm(anger ~ t + covid_cases_per_10000+lag(anger)+lag(anger,n=2L)+lag(anger,n=3L), family="poisson", data=df)
AIC(a3,k=5)

a4 <- glm(anger ~ t + covid_cases_per_10000+lag(anger)+lag(anger,n=2L)+lag(anger,n=3L)+lag(anger,n=4L), family="poisson", data=df)
AIC(a4,k=6)



```

## PLotting diagnostics

```{r}
vif(a0)
pacf(df$anger)
acf(df$anger)
dispersiontest(a0)
dispersiontest(a0,alternative = "less")

```

## Getting summary
```{r}
summary(a0)
```


